Wireless Automobile Detection, License Plate Processing, and Data Availability Network

### 2014-05-01 paper/paper.tex

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l || l | l | l |}
\hline
Data Set & Correct Recognition & Total Images & Percent Correct \\ \hline
Unaltered images & 12 & 41 & 29.27 \% \\ \hline
Cropped images & 4 & 52 & 7.69 \% \\ \hline
Compressed images & 4 & 27 & 14.81 \% \\ \hline
\end{tabular}
\end{center}
\caption{OpenALPR Results}
\end{table}

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l || l | l | l |}
\hline
Data Set & Correct Recognition & Total Images & Percent Correct \\ \hline
Unaltered images & 27 & 41 & 65.85 \% \\ \hline
Cropped images & 12 & 52 & 23.08 \% \\ \hline
Compressed images & 8 & 27 & 29.63 \% \\ \hline
\end{tabular}
\end{center}
\caption{Intrada ALPR Results}
\end{table}

\section{Future Research}
There is substantial future research that can be performed to add features and improve the efficacy of the system. This area of research appears very promising as similar systems may be applied and adapted to many different settings.

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l || l | l | l |}
\hline
Data Set & Correct Recognition & Total Images & Percent Correct \\ \hline
Unaltered images & 20 & 52 & 38.46 \% \\ \hline
Cropped images & 4 & 52 & 7.69 \% \\ \hline
Compressed images & 4 & 27 & 14.81 \% \\ \hline
\end{tabular}
\end{center}
\caption{OpenALPR Results}
\label{tab:openalprresults}
\end{table}

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l || l | l | l |}
\hline
Data Set & Correct Recognition & Total Images & Percent Correct \\ \hline
Unaltered images & 34 & 52 & 65.39 \% \\ \hline
Cropped images & 12 & 52 & 23.08 \% \\ \hline
Compressed images & 8 & 27 & 29.63 \% \\ \hline
\end{tabular}
\end{center}
\caption{Intrada ALPR Results}
\label{tab:intradaresults}
\end{table}
Three data sets were run through each ALPR system. As seen in Table \ref{tab:openalprresults} and Table \ref{tab:intradaresults}, Intrada ALPR outperformed OpenALPR in each case in terms of accuracy. In terms of speed, OpenALPR always outperformed Intrada ALPR by at least a factor of three. In some cases, OpenALPR was better by a factor of 110.

\begin{figure}
\begin{center}
\includegraphics[width=4.5in]{unexpectedrecognition}
\end{center}
\caption{The foreground license plate goes unrecognized in favor of a smaller plate in the background}
\label{fig:unexpectedrecognition}
\end{figure}

These results were calculated by determining whether or not the ALPR software correctly identified \emph{any} license plate in the photo. It is the case that, for certain out of state plates or nonstandard plates (e.g. Disabled Veteran), the ALPR programs will not identify the primary, or largest, license plate in the photo. However, both programs were successful in recognizing a much smaller, but standard, license plate. Figure \ref{fig:unexpectedrecognition} shows an example image where a New Mexico plate is ignored in favor of a smaller plate in the background.
\section{Future Research}
There is substantial future research that can be performed to add features and improve the efficacy of the system. This area of research appears very promising as similar systems may be applied and adapted to many different settings.

\subsection{ALPR Training}
The accuracy rate for our ALPR software is not as high as we had originally hoped it to be. OpenALPR offers a separate program, 'train-ocr' to help build definition files for certain geographic regions. Because it initially came seeded with training data for the entire continent, the recognition of Colorado plates may be improved if we create a training file for only Colorado.

Intrada ALPR cannot be configured by the end user (our team). We can, however, send sample images from our deployment to Q-Free, where our files can be used to train our account for better recognition.

Because we ended up using two ALPR systems instead of one, it would be beneficial to utilize both to provide a confidence level for our project. Having validation from both ALPRs would likely mean the characters that were extracted were correct. Extractions that were not correct could be flagged in the database for human intervention.

A proposed long-term goal for this project was to integrate license recognition with CSM's parking database to identify users who do not have valid parking permits. With the work that has been completed, we are now at a place where we could begin coding an interface to pass license data to Parking and Facilities.
